\title{Language and scientific explanation: Where does semantics fit in?}  %look no further, you can change those things right here.
% \subtitle{Change your subtitle in localmetadata.tex}
\BackTitle{Language and scientific explanation: Where does semantics fit in?} % Change if BackTitle != Title
\BackBody{This book discusses the two main construals of the explanatory goals of semantic theories. The first, externalist conception, understands semantic theories in terms of a hermeneutic and interpretive explanatory project. The second, internalist conception, understands semantic theories in terms of the psychological mechanisms in virtue of which meanings are generated. It is argued that a fruitful scientific explanation is one that aims to uncover the underlying mechanisms in virtue of which the observable phenomena are made possible, and that a scientific semantics should be doing just that. If this is the case, then a scientific semantics is unlikely to be externalist, for reasons having to do with the subject matter and form of externalist theories. It is argued that semantics construed hermeneutically is nevertheless a valuable explanatory project.
}
%\dedication{Change dedication in localmetadata.tex}
%\typesetter{Change typesetter in localmetadata.tex}
%\proofreader{Change proofreaders in localmetadata.tex}
\author{Eran Asoulin}
\BookDOI{10.5281/zenodo.3894134} %ask coordinator for DOI
\renewcommand{\lsISBNdigital}{978-3-96110-263-1}
\renewcommand{\lsISBNhardcover}{978-3-96110-264-8}
%\renewcommand{\lsISBNsoftcover}{000-0-000000-00-0}
%\renewcommand{\lsISBNsoftcoverus}{000-0-000000-00-0}
\renewcommand{\lsSeries}{cfls} % use lowercase acronym, e.g. sidl, eotms, tgdi
\renewcommand{\lsSeriesNumber}{5} %will be assigned when the book enters the proofreading stage
\renewcommand{\lsURL}{http://langsci-press.org/catalog/book/274} % contact the coordinator for the right number


\setlength{\csspine}{25.0559784mm} % Please calculate: Total Page Number (excluding cover, usually (Total Page - 3)) * 0.0572008 mm
\setlength{\bodspine}{20mm} % Please calculate: Total Page Number (excluding cover) * BODFACTOR + BODABS
